Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-04 doc/sc2012/soop.tex
figs

\begin{figure*}
\centering
\subfigure[Two independent {\tt calc\_new\_currents} tasks.]{
\label{fig:depexamp:a}
}
\subfigure[A {\tt distribute\_charge} task depends on the previous two.]{
\label{fig:depexamp:b}
}
\subfigure[An {\tt update\_voltages} task depends on the previous one.]{
\label{fig:depexamp:c}
}
\label{fig:depexamp}
\caption{Dependence analysis examples from {\tt circuit\_simulation}.}
\end{figure*}

>>>>

\begin{figure*}
\centering

\subfigure[Two {\tt calc\_new\_currents} tasks.]{
\includegraphics[scale=0.45]{figs/CNC_State.pdf}
\label{fig:depexamp:a}
}
\subfigure[{\tt distribute\_charge} depends on {\tt calc\_new\_currents}.]{ 
\includegraphics[scale=0.45]{figs/DC_state.pdf}
\label{fig:depexamp:b}
}
\subfigure[{\tt update\_voltages} depends on {\tt distribute\_charge}.]{
\includegraphics[scale=0.45]{figs/UV_State.pdf}
\label{fig:depexamp:c}
}
\subfigure[An {\tt update\_voltages} mapping.]{
\includegraphics[scale=0.45]{figs/UV_Update.pdf}
\label{fig:depexamp:d}
}
\label{fig:depexamp}
\caption{Dependence analysis examples from {\tt circuit\_simulation}.}
\end{figure*}
